\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.1cm]{geometry} % Marges réduites
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{mathpazo}
\usepackage[sfdefault]{FiraSans}
\usepackage{array}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\usepackage{hyperref}
\definecolor{mainblue}{HTML}{2E86C1}
\definecolor{graytext}{HTML}{555555}
\usepackage{sectsty}
\sectionfont{\color{mainblue}\fontsize{11}{11}\selectfont}
\subsectionfont{\color{mainblue}\fontsize{10}{10}\selectfont}
\hypersetup{
    colorlinks=true,
    linkcolor=mainblue,
    urlcolor=mainblue,
    citecolor=mainblue
}
% Espacement vertical entre les sections réduit
\titlespacing*{\section}{0pt}{5pt}{5pt}
\titlespacing*{\subsection}{0pt}{3pt}{3pt}
\setlist[itemize]{leftmargin=*, topsep=1pt, itemsep=1pt}
\linespread{0.98} % Légère compression verticale du texte

\begin{document}

\hyphenpenalty=10000
\exhyphenpenalty=10000
\sloppy

% === En-tête : bloc horizontal bien aligné ===
\begin{flushleft}
    {\Large \textbf{Neyl GASMI}} \\[0.2em]
    {\small 29 rue Villiers, Neuilly-Sur-Seine  \\
    \href{mailto:neylgasmi@gmail.com}{neylgasmi@gmail.com}} \\
\end{flushleft}



\vspace{0.5em}

\hrule
\vspace{1em}

% === Corps du CV en deux colonnes ===
\begin{minipage}[t]{0.45\textwidth}


\section*{Education}

\textit{2025–2026} \textbf{Université Paris-Dauphine — Paris} \\
Bachelor in Mathematics, Finance \& Actuarial Science \\
\textit{Focus:} Optimisation, Derivatives, Statistical Modelling, Machine Learning, Linear Programming, Microeconomics, Quantitative Methods for Finance, R \& Python programming

\vspace{0.8em}

\textit{2024–2028} \textbf{EDHEC Business School — Lille} \\
Msc Grande École Programme  \\
\textit{Focus:} Corporate Finance, Equity Valuation, Mergers \& Acquisitions, Financial Statement Analysis, Capital Markets Economics

\vspace{0.8em}

\textit{2024–2025} \textbf{Université de Lille} \\
Bachelor in Mathematics — Advanced Research Track \\
Ranked 2/57
\textit{Focus:} Probability, Statistics, Numerical Analysis, Optimisation, Differential Equations

\vspace{0.8em}

\textit{2021–2024} \textbf{Classes Préparatoires — Lycée Notre-Dame de Sion, Marseille} \\
Intensive programme in Mathematics \& Physics (MPSI/MP) \\
\textit{Ranked top 10\% of cohort; prepared for France’s Grandes Écoles competitive exams}

\vspace{0.8em}

\textit{2020–2021} \textbf{Lycée Périer — Marseille} \\
French Scientific Baccalauréat — \textit{Mention Bien} (Honours)

\section*{Skills}

\noindent
\textbf{Finance:} Market microstructure, equities/ETFs trading dynamics, derivatives pricing, execution quality, and liquidity fragmentation analysis.  

\vspace{0.3em}

\noindent
\textbf{Analytical \& Technical:} Large-scale Data Analysis (Python, SQL, PySpark), Research with high-frequency datasets, Machine Learning (Scikit-Learn, Clustering), and data visualisation (Matplotlib, Power BI), R.

\vspace{0.3em}

\noindent
\textbf{Mathematics:} Probability and statistics, stochastic processes, optimisation, econometrics, and quantitative methods for finance.  

\vspace{0.3em}

\noindent
\textbf{Languages:} French (native), English (C1), Arabic (conversational), Spanish (intermediate).  


\section*{Personal Qualities}
\begin{itemize}[leftmargin=*]
   \item \textbf{Analytical mindset} — able to synthesise complex financial data into clear insights for decision-making.  
   \item \textbf{Rigour and attention to detail} — ensuring accuracy under tight deadlines and high transaction volumes.  
   \item \textbf{Adaptability} — quickly integrate into fast-paced deal environments and cross-border teams.  
   \item \textbf{Communication skills} — confident in presenting ideas and collaborating with diverse stakeholders.  
   \item \textbf{Initiative and reliability} — proactive in problem-solving, dependable in team delivery.  
\end{itemize}



\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}

\section*{Professional Experience}

{\bfseries Research Intern – EuroCTP, ESMA Consolidated Tape Candidate for Equities \& ETFs, Amsterdam}~% 
\\
\textit{June–August 2025}
\begin{itemize}
    \item Researched predictive microstructure signals by extracting and analysing \textbf{Level 1–3 datasets} (billions of daily order book updates), applying time-series statistics to study liquidity fragmentation, volatility clustering, and trading cost dynamics.  
\item Analaysed microstructure behaviour across \textbf{20+ European venues}, quantifying latency asymmetries, liquidity fragmentation, and volume concentration to generate systematic insights into market efficiency.
    \item Developed \textbf{Python pipelines and research tools} to process large-scale structured/unstructured data, enabling reproducible signal testing and scalable performance benchmarking by MIC and instrument.  
    \item Implemented \textbf{machine learning–inspired anomaly detection and clustering} methods to validate data integrity and uncover patterns in market activity, improving robustness of research inputs.  
    \item Enhanced the research infrastructure by building automated dashboards and libraries for throughput, latency, and cross-venue attribution, supporting both regulatory analysis and systematic strategy development.  
\end{itemize}



\vspace{0.6em}
\textbf{Client Advisor – Galeries Lafayette, Marseille} \\
\textit{Summers 2022–2024}
\begin{itemize}
    \item Managed relationships with high-value clients, delivering discretion, service quality, and commercial outcomes.
\end{itemize}

\vspace{0.4em}
\textbf{Mathematics Tutor}  \\
\textit{2019 – Today} 
\begin{itemize}
	\item Prepared students for competitive exams and university-level quantitative courses.
\end{itemize}

\section*{Certifications}
\begin{itemize}[leftmargin=*]
    \item \textbf{CFA Level I Candidate} — Exam scheduled February 2026  
    \item \textbf{TOEIC} 915/990  
    \item \textbf{TOSA Excel} 700/1000  
    \item \textbf{PIX} (Numerical Skills)  
\end{itemize}
\vspace{0.4em}

\section*{Interests}
\begin{itemize}[leftmargin=*]
\item \textbf{Astronomy:} Strong interest in celestial phenomena and long-term observational cycles.  
\item \textbf{Mathematics:} Attended advanced conferences at CIRM — often beyond my grasp, but always inspiring.  
\item \textbf{Reading:} Regular commitment to reading, averaging 10 books per year across diverse genres.  
\item \textbf{Sailing:} Experienced navigator in the Calanques National Park.  

   \end{itemize}



\end{minipage}

\end{document}
